### 2013-12-19 paper/main.tex
added Colophon
A Colophon has been added that describes how this
document was designed.  The References section has
also moved to the end of the document.

@@

>>>>

% TODO

@@

% {{{ Colophon
\clearpage
\section{Colophon}
\label{app:colophon}

This written in \LaTeX and built using Pdflatex.
The block diagrams were written using TikZ\autocite{tikz}.
All calculations and plots were run using version 3.6.4 of
Octave\autocite{octave}, an open source Matlab clone.
When possible the examples were tested in Matlab/Simulink.
However much of the code is dependent upon the
Octave Control (CACSD) Tools\autocite{octave-control} which are
not entirely compatible with Matlab.
This document and all of its code are released under the
GNU General Public License and freely
available\autocite{github_jmahler_idle-control}.
\nocite{github_jmahler_control}
